Gas Dynamics of the Einstein ring RXSJ1131-1123 at $z$=0.654

### 2016-05-15 WRITEUP/ms.tex
done HST astroemtry sec

% Done: PdBI observations, VLA observations, CARMA obs
%
%
%
%
%

@@

Observations were carried out on 2008 December 29 under excellent weather
conditions in the A array configurations for a total of $\sim$7 hours on-source time. The C-Band receivers were used with a continuum mode setup, providing a bandwidth of 50
MHz in each sideband.
The nearby radio quasar 1130$-$149 was observed every 10 minutes for
pointing, amplitude, and phase calibration, 1331$-$305 was observed as the
primary flux calibrator, and 0319$+$415 was observed as the bandpass calibrator, yielding $\sim$10\% calibration accuracy.
We use \aips to calibrate the visibility data which
are then imaged and deconvolved using
the CLEAN algorithm using robust\,=\,0. This yields a synthesized clean
beam size of 0$\farcs$49 $\times$ 0\farcs35 (PA\,=\, 0\farcs18) and a final
rms noise of $\sigma$ = 13 $\mu$Jy beam\pmOne.

\section{HST astrometry}
We gathered optical (rest-frame UV) images for RXJ1131 from the Hubble Legacy Archive to illustrate the
spatial extent of different emission detected in this paper. Here, we only use the F555W image for
this purpose.
We adopt the VLA 5\,GHz map of $\sim$2" resolution as the reference coordinate frame to align the optical image.
We shifted the latter to the east by 0\farcs5963 in R.A. and +0\farcs8372 in Dec., which is consistent with the typical astrometric precision of the HST image from the Hubble
Legacy Archive. % for Hubble Legacy Archive: abs. astronmetry 1-2" http://hla.stsci.edu/hla_faq.html
The radio image is calibrated employing well-monitored phase calibrator, with positions known to $\sim$1 mas.
We estimate the absolute alignment of the 5 GHz and CO(J=2-1) coordinate frames should
be better than 0.1", leaving aside uncertainties relating to the SNR and beam size.

%The astrometry of the HST images was firstly calibrated against a wider-field
%optical image of the cluster which had in turn been aligned onto the FK5
%coordinate system to an rms precision of ~0.2".

@@

%--------------------------------------------------------------------------
%                                Discussion
%--------------------------------------------------------------------------
\section{Discussion}
\subsection{At what stage is the merging in RXJ1131-1231?}

\subsection{Implications} gas fraction at this redshift. how does that relate to
the SFH. --> imply the change in cosmic SFD is due to change in gas content. SFE
at this redshift, how does that relate to the SFH. probably a secondary effect
to the drop in SFH

  %--------------------------------------------------------------------------
%                                Conclusions
%--------------------------------------------------------------------------
\section{Summary and Conclusions}
We studied a wet-wet merger between a AGN/starburst ULIRG and a optically faint companion at $z$ $\sim$ 0.65.

>>>>

% Done: PdBI observations, VLA observations, CARMA obs, HST astrometry
%
%
%
%
%

@@

Observations were carried out on 2008 December 29 under excellent weather
conditions in the A array configurations for a total of $\sim$7 hours on-source time. The C-Band receivers were used with a continuum mode setup,
providing a bandwidth of 50 MHz in each sideband.
The nearby radio quasar 1130$-$149 was observed every 10 minutes for
pointing, amplitude, and phase calibration, 1331$-$305 was observed as the
primary flux calibrator, and 0319$+$415 was observed as the bandpass
calibrator, yielding $\sim$10\% calibration accuracy.
We use \aips to calibrate the visibility data which
are then imaged and deconvolved using
the CLEAN algorithm using robust\,=\,0. This yields a synthesized clean
beam size of 0$\farcs$49 $\times$ 0\farcs35 (PA\,=\,0\farcs18) and a final
rms noise of $\sigma$ = 13 $\mu$Jy beam\pmOne.

\section{HST astrometry}
We obtain HST images from the Hubble Legacy Archive with
a goal to understand the origins of the emission detected
in our mm observations. We adopt the VLA 5\,GHz map of $\sim$0\farcs5
resolution as the reference coordinate frame to align the optical (V-band)image
. We shift the latter to the east by 0\farcs5963 in R.A. and +0\farcs8372 in
Dec., which is consistent with the typical astrometric precision (1$-$2") of
images from the Hubble Legacy Archive\footnote{http://hla.stsci.edu/hla_faq.
html}. Such astrometric correction is critical to avoid artificial spatial
offsets between emission and to carry out our lens modeling, as the absolute
position of the foreground lensing galaxy is guided by its coordinates in the
optical image, where its emission is clearly detected.
The VLA image is calibrated using a well-monitored phase
calibrator, with absolute positional accuracy of $\sim$2 mas.
For this reason, the absolute alignment between the VLA image and other
interferometric images reported in this paper are expected to have astrometric
precision better than 0\farcs1, modulo uncertainties related to the SNR, phase
errors, and beam size.

@@

%--------------------------------------------------------------------------
%                                Discussion
%--------------------------------------------------------------------------
\section{Discussion}
\subsection{Merger stage of RXJ1131-1231}

\subsection{Implications} gas fraction at this redshift. how does that relate to
the SFH, this implies the change in cosmic SFD is due to change in gas content. SFE
at this redshift, how does that relate to the SFH. probably a secondary effect
to the drop in SFH

  %--------------------------------------------------------------------------
%                                Conclusions
%--------------------------------------------------------------------------
\section{Summary and Conclusions}
We studied a wet-wet merger between a AGN/starburst ULIRG and a optically faint companion at $z$ $\sim$ 0.65.
In this paper, we BLAH, refining the redshift to $z_{\rm CO}$=0.65370$\pm$0.0005
